\sysfull

### 2018-08-05 paper/asplos19/background.tex
SIunits package errors fixed

\textbf{Incorrectly Sized Tasks Problem.} Compiler-inserted checkpoints or
programmer-defined tasks can be both non-terminating and/or
inefficient.  If a task (or code between two checkpoints) consumes more than the fixed,
maximum energy that the device can buffer, then the task
will never be able to complete using buffered energy only.  Such a task is
non-terminating, {\em prevents forward progress}, and makes the program
deadlock. 
%
If the task consumes far less energy than a device can buffer, the system
may operate {\em inefficiently}, saving the program state more often than needed.
%
Avoiding excessively costly, non-terminating, tasks and short, high-overhead,
tasks is challenging, because estimating the exact energy use of an arbitrary code is complicated.  
Moreover, when \emph{heterogeneous devices} with different energy buffers (e.g., 20 \micro\farad~\cite{rodriguez_tbcs_2015} to 0.1 \farad~\cite{moo}) are considered, the problem of porting a program becomes much worse
because a large task on one device may be a relatively short task
on a device with a larger buffer.
%
\textbf{\sys's execution model} solves this dilemma by introducing {\em task coalescing}, which
merges multiple tasks to amortize the overhead when tasks are too small, and
{\em task downscaling}, which breaks up a task when it is too large to complete.

>>>>

\textbf{Incorrectly Sized Tasks Problem.} Compiler-inserted checkpoints or
programmer-defined tasks can be both non-terminating and/or
inefficient.  If a task (or code between two checkpoints) consumes more than the fixed,
maximum energy that the device can buffer, then the task
will never be able to complete using buffered energy only.  Such a task is
non-terminating, {\em prevents forward progress}, and makes the program
deadlock. 
%
If the task consumes far less energy than a device can buffer, the system
may operate {\em inefficiently}, saving the program state more often than needed.
%
Avoiding excessively costly, non-terminating, tasks and short, high-overhead,
tasks is challenging, because estimating the exact energy use of an arbitrary code is complicated.  
Moreover, when \emph{heterogeneous devices} with different energy buffers (e.g., 20 \si{\micro\farad}~\cite{rodriguez_tbcs_2015} to 0.1 \si{\farad}~\cite{moo}) are considered, the problem of porting a program becomes much worse
because a large task on one device may be a relatively short task
on a device with a larger buffer.
%
\textbf{\sys's execution model} solves this dilemma by introducing {\em task coalescing}, which
merges multiple tasks to amortize the overhead when tasks are too small, and
{\em task downscaling}, which breaks up a task when it is too large to complete.

### 2018-08-05 paper/asplos19/intro.tex
SIunits package errors fixed

%%%%%%%%%%%%%%%%%%%%%% IMPORTANT INFO %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% SRAM read/write latency is in the order of 8ns 		 [ Intermittent computation without hardware support of programmer intervention]
% FRAM read/write latency is in the orfer of 60ns/100ns  [Texas Instrument MSP430FR573x DataSheet]
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
Advances in processor efficiency along with the development of
energy-harvesting systems have created a new category of devices that require
neither a battery nor a tethered power
supply~\cite{prasad_comst_2014,lucia_snapl_2017,soyata_csm_2016}. These
devices operate using ambient energy, such as radio frequency
transmissions~\cite{rf_powered_computing_gollakota_2014},
light~\cite{margolies_infocom_2016,margolies_tosn_2016}, and
vibration~\cite{gorlatova_sigmetrics_2014}. Incorporating compute, storage,
sensing, and communication hardware~\cite{wisp5,moo,capybara}, such devices are a
promising technology for use in the Internet of Things~\cite{ku_cst_2016},
in-body~\cite{nadeau_naturebio_2017} and
on-body~\cite{bandodkar_electroanalysis_2015} medical systems, and
energy-harvesting nano-satellites~\cite{kicksat,capybara}.
%
Energy-harvesting devices create unique challenges because they operate {\em
intermittently} when energy is
available~\cite{hicks_isca_2017,lucia_snapl_2017}. An energy-harvesting device
buffers energy in a small storage capacitor~\cite{gorlatova_tmc_2013,gunduz_commag_2014} and operates when a
threshold amount of energy has accumulated. Harvestable energy sources are low-power (e.g., \nano\watt\ to \micro\watt) compared to a platform's operating
power level (hundreds of \micro\watt\ to \milli\watt). A device operates briefly until it depletes its buffered energy, after which, it shuts
down and recharges to operate again later---corresponding to the {\em intermittent execution model}~\cite{dino,lucia_snapl_2017} composed of
operation-power failure-restart cycles. 
The recharge and discharge intervals---which correspond to the device's inactive and active time---vary with the energy buffering capacitor~\cite{capybara} \note{not only, though} and some devices fail and restart operating $\approx$10 to
$\approx$100 times per second~\cite{tan_infocom_2016,mementos,nvp}.
%
%\textbf{Data Consistency in Intermittent Computing.}

>>>>

%%%%%%%%%%%%%%%%%%%%%% IMPORTANT INFO %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% SRAM read/write latency is in the order of 8ns 		 [ Intermittent computation without hardware support of programmer intervention]
% FRAM read/write latency is in the orfer of 60ns/100ns  [Texas Instrument MSP430FR573x DataSheet]
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
Advances in processor efficiency along with the development of
energy-harvesting systems have created a new category of devices that require
neither a battery nor a tethered power
supply~\cite{prasad_comst_2014,lucia_snapl_2017,soyata_csm_2016}. These
devices operate using ambient energy, such as radio frequency
transmissions~\cite{rf_powered_computing_gollakota_2014},
light~\cite{margolies_infocom_2016,margolies_tosn_2016}, and
vibration~\cite{gorlatova_sigmetrics_2014}. Incorporating compute, storage,
sensing, and communication hardware~\cite{wisp5,moo,capybara}, such devices are a
promising technology for use in the Internet of Things~\cite{ku_cst_2016},
in-body~\cite{nadeau_naturebio_2017} and
on-body~\cite{bandodkar_electroanalysis_2015} medical systems, and
energy-harvesting nano-satellites~\cite{kicksat,capybara}.
%
Energy-harvesting devices create unique challenges because they operate {\em
intermittently} when energy is
available~\cite{hicks_isca_2017,lucia_snapl_2017}. An energy-harvesting device
buffers energy in a small storage capacitor~\cite{gorlatova_tmc_2013,gunduz_commag_2014} and operates when a
threshold amount of energy has accumulated. Harvestable energy sources are low-power (e.g., \si{\nano\watt}\ to \si{\micro\watt}) compared to a platform's operating
power level (hundreds of \si{\micro\watt}\ to \si{\milli\watt}). A device operates briefly until it depletes its buffered energy, after which, it shuts
down and recharges to operate again later---corresponding to the {\em intermittent execution model}~\cite{dino,lucia_snapl_2017} composed of
operation-power failure-restart cycles. 
The recharge and discharge intervals---which correspond to the device's inactive and active time---vary with the energy buffering capacitor~\cite{capybara} \note{not only, though} and some devices fail and restart operating $\approx$10 to
$\approx$100 times per second~\cite{tan_infocom_2016,mementos,nvp}.
%
%\textbf{Data Consistency in Intermittent Computing.}
